\documentclass[10.7pt]{article}  % Use 14pt as the base font size
\usepackage[a4paper,left=0.5in,right=0.5in,top=1cm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{url}
\usepackage{enumitem}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{textcomp}
% Rest of your packages and configurations

% Adjusting the margins
\enlargethispage{6\baselineskip} % Change the value as per your comfort

%for color
\usepackage[usenames, dvipsnames]{color}
\definecolor{myblue}{RGB}{10,0,254}

\newcommand{\xfilll}[2][1ex]{
\dimen0=#2\advance\dimen0 by #1
\leaders\hrule height \dimen0 depth -#1\hfill}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}
\renewcommand\labelitemi{\raisebox{0.4ex}{\tiny$\bullet$}}
\renewcommand{\labelitemii}{$\cdot$}
\pagenumbering{gobble}


\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.99}
\textheight=10in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[{\color[RGB]{10,0,254}$\bullet$}] #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.99\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{8.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}


\begin{document}
\begin{table}
    \begin{center}
    {\Huge \scshape Sharath Pai} \\ \vspace{1pt}
    FULL STACK DEVELOPER \& ML ENGINEER \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1-234-567-890 ~ \href{mailto:sharathpai107@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sharathpai107@gmail.com}} ~ 
    \href{https://linkedin.com/in/sharathpai107}{\raisebox{-0.2\height}\faLinkedin\ \underline{/sharathpai107}}  ~
    \href{https://github.com/Sharath1036}{\raisebox{-0.2\height}\faGithub\ \underline{/Sharath1036}} ~
    \href{https://sharathpai.vercel.app}{\raisebox{-0.2\height}\faGlobe\ \underline{/sharathpai.vercel.app}}
    \vspace{-8pt}
\end{center}
\end{table}    

\setlength{\tabcolsep}{25pt}
\begin{table}
\centering
\begin{tabular}{lllll}
\toprule
\textbf{Degree}   & \textbf{Institute}    & \textbf{Year}     & \textbf{CPI/\%} \\ 
\toprule
% Post Graduation & IIT Bombay    & IIT Bombay    & 2019-21   & 9.40\\ 
B.Tech (ECE) & D.J. Sanghvi College of Engineering  & 2020-2024   & 7.6\\ 
HSC          & Patkar Varde College & 2018-2020       & 83.23    \\ 
SSC    & Dr. S. Radhakrishnan Vidyalaya    & 2006-2018          & 90.80   \\
\bottomrule \\[-0.75cm]
\end{tabular}
\end{table}
% \fi 
\vspace{-8pt}

%%% SHORT SUMMARY %%%
\section*{{ \LARGE \color{myblue} Summary}\xfilll[0pt]{0.5pt}}
\vspace{-15pt}
\vspace{1.5mm}
An astute learner who is passionate about building websites and analysing data, I am dedicated towards my work and looking forward for collaborations in open source and opportunities that would help me in my growth as well as getting along in a team of skilled individuals.
\vspace{-8pt}

%%%% PROFESSIONAL EXPERIENCE %%%%
\section*{{\LARGE \color{myblue}Professional Experience}\xfilll[0pt]{0.5pt}}
\vspace{-15pt}
\vspace{1.5mm}
\setlist[itemize,1]{label={\color[RGB]{10,0,254}\large$\bullet$}} % Add this line to change the font size and color of list items

% Rest of your Professional Experience content


%\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\textbf{\large Web Development Intern}| \normalfont{Suvidha Foundation} \hfill {\ \small Sep 2023 - Oct 2023}
\\[-0.5cm]
% \emph{Awarded Letter of Recommendation for excellent performance during the internship period } 
\\[-0.6cm]	
	\begin{itemize}[itemsep = -0.75 mm]
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Working on a healthcare website project where people can monitor their health and book a doctor's appointment accordingly.
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent It is a \textbf{MERN Stack} Website in which I followed the Node MVC Architecture to create and integrate the Frontend and Backend of the website.
        \end{itemize} 

\vspace{-14pt}

%%% SKILLS %%%
\section*{{\LARGE \color{myblue}Technical Skills}\xfilll[0pt]{0.5pt}}

\vspace{-15pt}
\vspace{1.5mm}

\begin{itemize}[itemsep = -0.70 mm, leftmargin=*]

\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent \textbf{Programming:} 
C, JavaScript, R, Solidity, SQL %\LaTeX
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent \textbf{Development:} Bootstrap, ExpressJS, Handlebars, NodeJS, ReactJS
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent \textbf{Design:} 
Figma, Illustrator, Photoshop, Wordpress
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent \textbf{Tools:} 
Git, GitHub, MySQL, VSCode
\end{itemize}	

\vspace{-15pt}


%%% PROJECTS %%%
\section*{{ \LARGE \color{myblue} Projects}\xfilll[0pt]{0.5pt}}
\vspace{-15pt}
\vspace{1.5mm}

{\LARGE \textcolor{black}{Development}}
\vspace{-6.5pt}
\par\noindent\hrulefill % Add a horizontal line
\\[0.15cm]
%\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\textbf{\large{Science Mission Website}}| \normalfont{ExpressJS, Handlebars} \hfill {\ \small Ongoing} 
\\[0.05cm]
\emph{Science Mission, Dallas, USA} \hfill {\ \small (Expected by Mar '24)}
\\[-0.6cm]	
	\begin{itemize}[itemsep = -0.75 mm]
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Creating a freelance website that contains several articles related to science along with the videos as remedy.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Each article has its own category and the user can filter out the articles based on their choice of category.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent I am creating the \textbf{backend} routes using \textbf{ExpressJS} and using the \textbf{Handlebars} template engine for the \textbf{design}.
	\end{itemize}
\textbf{\large{Blogpage}}| \normalfont{ExpressJS, Handlebars} \hfill {\ \small Sep 2023}
\\[0.05cm]
\emph{Self Project} \hfill {\href{https://sharathblogs.vercel.app}{\underline{Project Link} }
\\[-0.6cm]	
	\begin{itemize}[itemsep = -0.75 mm]
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Created a blogpage in which showcase my written blogs.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent I am thinking of converting this website to a \textbf{dynamic website} in which the user can create and publish their own blogs in which the data can be dynamically passed through a database, preferrably Mongoose.
	\end{itemize} 
\textbf{\large{Swift UnderGrads Website}}| \normalfont{ReactJS} \hfill {\ \small Jul 2023}
\\[0.05cm]
\emph{Swift UnderGrads} \hfill {\href{https://www.swiftundergrads.in}{\underline{Project Link} }
\\[-0.6cm]	
	\begin{itemize}[itemsep = -0.75 mm]
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Developed a fully responsive \textbf{Frontend} educational website for our community which helps students in getting their desired study material.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent It is a static website  and further I am planning to create a portal for various events conducted by the team and a \textbf{blockchain} powered \textbf{payment gateway} for secure transactions.
	\end{itemize} 
{\LARGE \textcolor{black}{Data Science \& Machine Learning}}
\vspace{-6.5pt}
\par\noindent\hrulefill % Add a horizontal line
\\[0.15cm]
\textbf{\large{Analysis of House Price}}| \normalfont{R} \hfill {\ \small Apr 2023}
\\[0.05cm]
\emph{Self Project} \hfill {\href{https://github.com/Sharath1036/house-price-analysis}{\underline{Project Link} }
\\[-0.6cm]	
	\begin{itemize}[itemsep = -0.75 mm]
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent First, the data from the dataset is \textbf{preprocessed }to remove outliers and impute missing variables.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent In the \textbf{Regression} model, we determine which variables significantly impact the \textbf{house price as a dependent variable} and obtain its mathematical equation.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent In the \textbf{Classification} model, we determine whether a house will be sold in 3 months or not. We used \textbf{test-train spli}t and outputted the \textbf{confusion matrix }of various algorithms on the test set and found out that the \textbf{Linear Discriminant Analysis} gives us the highest accuracy of \textbf{66.6\%}.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent The dataset used here is \textbf{Boston Housing Dataset} which is available on Kaggle.
	\end{itemize} 
 \textbf{\large{Analysis of Movies}}| \normalfont{R} \hfill {\ \small Oct 2023}
\\[0.05cm]
\emph{Self Project} \hfill {\href{https://github.com/Sharath1036/movie-analysis}{\underline{Project Link} }
\\[-0.6cm]	
	\begin{itemize}[itemsep = -0.75 mm]
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent In this project we use \textbf{Decision Trees}, \textbf{Ensembling techniques} and \textbf{Support Vector Machines} to determine the outcome.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent First, the data from the dataset is \textbf{preprocessed }to remove outliers and impute missing variables.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent In the \textbf{Regression} model, we predict the box office collection by splitting the dataset into training and test data and find the mean squared error to check the accuracy of each model. Here the \textbf{Random Forest Algorithm} provides the least error rate of \textbf{41 million}.
        \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent In the \textbf{Classification} model, we check whether the movie has received an Oscar or not and. Using the test train split and finding the confusion matrix of each model, the \textbf{XG boost} technique provides the highest accuracy of \textbf{65\%}.
        
	\end{itemize} 
\vspace{-15pt}

%%% PUBLICATIONS %%%
\section*{{\LARGE \color{myblue}Publications}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\textbf{\large{Audio Source Separation as applied to Vocals-Accompaniment Separation}} \hfill {\ \small Mar 2022}
\\[0.05cm]
\emph{DJS Strike} \hfill{\small ISBN: 978-93-5578-944-0}
\\[-0.6cm]
\begin{itemize}[itemsep = -0.75 mm]
    \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent The objective of this paper is to present a system for extracting the vocals from any track composed of vocals, instruments and computerized sound effects.
    \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent The training dataset is composed of the tracks for the composite 'mix' and the accompanying vocals.
    \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent The output audio is obtained by \textbf{postprocessing} this spectrogram using the inverse short-time \textbf{Fourier transform} amongst other techniques.
\end{itemize}

%%% COURSES %%%
\section*{{\LARGE \color{myblue}Key Courses Undertaken}\xfilll[0pt]{0.5pt}}
\vspace{-15pt}
\vspace{1.5mm}

%\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\textbf{\large Mathematics and Statistics}
\\[-0.6cm]
\begin{itemize}
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Calculus, Probability and Random Processes, Basics of Statistics, Data Preprocessing for Regression Analysis, Regression Models, Classification Models, Ensemble Techniques, Support Vector Machines, Artificial Neural Networks, Convolutional Neural Networks, Transfer Learning, Time Series
	\end{itemize}
\textbf{\large Computer Science}
\\[-0.6cm]
\begin{itemize}
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Structured Programming Approach, Data Structures and Algorithms, Operating Systems, Computer Networks
	\end{itemize}
\vspace{-15pt}


%%% POSITIONS OF RESPONSIBILITY %%%
 \section*{{\LARGE \color{myblue}Positions of Responsibility}\xfilll[0pt]{0.5pt}}
\vspace{-15pt}
\vspace{1.5mm}

\textbf{\large{Founder \& Tech Lead}}} \hfill {\ \small Feb 2022 - Present}
\\[0.05cm]
\emph{Swift UnderGrads}
\\[-0.6cm]
\begin{itemize}[itemsep = -0.75 mm]
    \item[{\color[RGB]{10,0,254}$\bullet$}] \noindent A community running of telegram, we aim to help \textbf{MHT-CET aspirants} by guiding them regarding further admission process.
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent I lead a \textbf{team of 12 members}, all belonging to different areas in Maharashtra. My job is to mentor aspirants and look after the social handles.  
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent We conduct various \textbf{webinars} to help students with their studies and make them clear about the admission process and further career opportunities. Till now we have helped \textbf{1000+} students in their journey.
	\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent I also \textbf{created a website} which helps students to get their desired study materials.
	\end{itemize}
\textbf{\large{Head of Public Relations \& Social Media}}} \hfill {\ \small Nov 2021 - Apr 2023}
\\[0.05cm]
\emph{DJSCE IETE}
\\[0.3cm]
\textbf{\large{Head of Graphics}}} \hfill {\ \small Mar 2022 - Oct 2022}
\\[0.05cm]
\emph{DJS eXpress}
\\[0.1cm]
\vspace{-15pt}

%%% ACHIEVEMENTS %%%
\section*{{\LARGE \color{myblue}Achievements \& Certifications}\xfilll[0pt]{0.5pt}}
\vspace{-15pt}
\vspace{1.5mm}

\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Runner Up in \textbf{DJS Strike} Innovative Project Development 2022 Competition.
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Finalist in Pixel Paranoia \textbf{UI/UX} Hackathon.
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Completed 30 Days of \textbf{Google Cloud}.
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent Certification in 30 Days of \textbf{Solidity} Challenge.
\item[{\color[RGB]{10,0,254}$\bullet$}] \noindent 5 stars in \textbf{Hackerrank C}.
\end{itemize}

\end{document}
